\bf The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-03-08 paper/forestecology.Rmd
typos

---
title: The forestecology R package for fitting and assessing nieghborhood models of the effect of interspecific competition on the growth of trees

@@

where the null hypothesis $H_0$ reflects a hypothesis of no species grouping-specific effects of competition while the alternative hypothesis $H_A$ reflects a hypothesis of species grouping-specific effects of competition. Furthermore, in order to account for the spatial autocorrelation inherent to forest data in their estimates of out-of-sample model error, @allen_permutation_2020 use spatial cross-validation. Estimates of model error that do not account for this spatial dependency tend to underestiamte the true model error [@roberts_cross-validation_2017].

>>>>

---
title: The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

@@

where the null hypothesis $H_0$ reflects a hypothesis of no species grouping-specific effects of competition while the alternative hypothesis $H_A$ reflects a hypothesis of species grouping-specific effects of competition. Furthermore, in order to account for the spatial autocorrelation inherent to forest data in their estimates of out-of-sample model error, @allen_permutation_2020 use spatial cross-validation. Estimates of model error that do not account for this spatial dependency tend to underestimate the true model error [@roberts_cross-validation_2017].

### 2021-03-08 paper/forestecology.tex
typos

\if0\blind
{
  \title{\bf The forestecology R package for fitting and assessing nieghborhood
models of the effect of interspecific competition on the growth of trees}

@@

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf The forestecology R package for fitting and assessing nieghborhood
models of the effect of interspecific competition on the growth of trees}
  \end{center}
  \medskip
} \fi

@@

where the null hypothesis \(H_0\) reflects a hypothesis of no species
grouping-specific effects of competition while the alternative
hypothesis \(H_A\) reflects a hypothesis of species grouping-specific
effects of competition. Furthermore, in order to account for the spatial
autocorrelation inherent to forest data in their estimates of
out-of-sample model error, \citet{allen_permutation_2020} use spatial
cross-validation. Estimates of model error that do not account for this
spatial dependency tend to underestiamte the true model error
\citep{roberts_cross-validation_2017}.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi}
\CommentTok{## # A tibble: 6,296 x 8}
\CommentTok{##   focal_ID focal_sp   dbh foldID                  geometry growth comp }
\CommentTok{##      <dbl> <fct>    <dbl> <fct>                    <POINT>  <dbl> <lis>}
\CommentTok{## 1        4 nysy     13.6  1                     (14.2 428)  0.103 <tib~}
\CommentTok{## 2        5 havi      8.8  1                      (9.4 436)  0.150 <tib~}
\CommentTok{## 3       79 tiam     47.7  1                       (40 381) -0.161 <tib~}
\CommentTok{## 4       80 caca      5.15 1                     (38.7 422)  0.253 <tib~}
\CommentTok{## 5       96 libe      2.3  1                       (60 310)  0.262 <tib~}
\CommentTok{## # ... with 6,291 more rows, and 1 more variable: growth_hat <dbl>}
\end{Highlighting}
\end{Shaded}

>>>>

\if0\blind
{
  \title{\bf The forestecology R package for fitting and assessing neighborhood
models of the effect of interspecific competition on the growth of trees}

@@

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf The forestecology R package for fitting and assessing neighborhood
models of the effect of interspecific competition on the growth of trees}
  \end{center}
  \medskip
} \fi

@@

where the null hypothesis \(H_0\) reflects a hypothesis of no species
grouping-specific effects of competition while the alternative
hypothesis \(H_A\) reflects a hypothesis of species grouping-specific
effects of competition. Furthermore, in order to account for the spatial
autocorrelation inherent to forest data in their estimates of
out-of-sample model error, \citet{allen_permutation_2020} use spatial
cross-validation. Estimates of model error that do not account for this
spatial dependency tend to underestimate the true model error
\citep{roberts_cross-validation_2017}.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi}
\CommentTok{## # A tibble: 6,296 x 8}
\CommentTok{##   focal_ID focal_sp   dbh foldID   geometry growth comp             }
\CommentTok{##      <dbl> <fct>    <dbl> <fct>     <POINT>  <dbl> <list>           }
\CommentTok{## 1        4 nysy     13.6  1      (14.2 428)  0.103 <tibble [20 x 4]>}
\CommentTok{## 2        5 havi      8.8  1       (9.4 436)  0.150 <tibble [32 x 4]>}
\CommentTok{## 3       79 tiam     47.7  1        (40 381) -0.161 <tibble [20 x 4]>}
\CommentTok{## 4       80 caca      5.15 1      (38.7 422)  0.253 <tibble [12 x 4]>}
\CommentTok{## 5       96 libe      2.3  1        (60 310)  0.262 <tibble [14 x 4]>}
\CommentTok{## # ... with 6,291 more rows, and 1 more variable: growth_hat <dbl>}
\end{Highlighting}
\end{Shaded}
